Geometric Control for Autonomous Landing on Asteroids

### 2017-08-10 manuscript.tex
Use subcaptionbox

The simulation is carried out over \SI{7200}{\second} with the spacecraft following a circular trajectory for the first \SI{3600}{\sec} before vertically descending in the body fixed frame for the last \SI{3600}{\second}.
\Cref{fig:true_landing_trajectory} shows a view from the positive \( \vb{f}_3 \) pole of the asteroid of the simulated trajectory. 
The position of the center of mass of the dumbbell is shown in blue, while the pointing direction of the camera view axis is defined in red. 
The attitude of the dumbbell is displayed at several points along the trajectory demonstraiting the pointing of the camera. 
Furthermore, asteroid Itokawa is shown in it's final orientation at the completion of the landing simulation. 
\Cref{fig:pos_components} shows that the nonlinear controller is able to accurately track the desired translational trajectory for the duration of the simulation.
\begin{figure}[htbp]
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/traj_fig.pdf} 
        \caption{Planar view of landing trajectory\label{fig:true_landing_trajectory}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/pos_fig.pdf} 
        \caption{Position of spacecraft in the inertial frame\label{fig:pos_components}} 
    \end{subfigure} 
    \caption{Landing trajectory to asteroid Itokawa~\label{fig:position}}
\end{figure}

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one exampel view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~\cref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
From these tracked features it is possible to estimate the relative motion of the camera~\cite{szeliski2010}.
\Cref{fig:orbslam_localization} shows a visualization of the localization process from the imagery. 
Through monocular images it is not possible to compute the position of the camera relative to the inertial frame.
Rather, it is only possible to determine a camera pose accurate to an unknown scale factor. 
This limitation is intrinsic to the transformation of the three-dimensional scene onto the two-dimensional image plane~\cite{szeliski2010}.
However, it is possible to compute the relative motion between sequential images and we use this to estimate the motion of the camera.
\begin{figure}[htbp]
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/orbslam_mappoints.png} 
        \caption{ORB-SLAM2 Feature Tracking Visualization\label{fig:orbslam_mappoints}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/orbslam_localization.png} 
        \caption{ORB-SLAM2 Localization from monocular images \label{fig:orbslam_localization}} 
    \end{subfigure} 
\end{figure}

>>>>

The simulation is carried out over \SI{7200}{\second} with the spacecraft following a circular trajectory for the first \SI{3600}{\sec} before vertically descending in the body fixed frame for the last \SI{3600}{\second}.
\Cref{fig:true_landing_trajectory} shows a view from the positive \( \vb{f}_3 \) pole of the asteroid of the simulated trajectory. 
The position of the center of mass of the dumbbell is shown in blue, while the pointing direction of the camera view axis is defined in red. 
The attitude of the dumbbell is displayed at several points along the trajectory demonstraiting the pointing of the camera. 
Furthermore, asteroid Itokawa is shown in it's final orientation at the completion of the landing simulation. 
\Cref{fig:pos_components} shows that the nonlinear controller is able to accurately track the desired translational trajectory for the duration of the simulation.
\begin{figure}[htbp]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{Planar view of landing trajectory\label{fig:true_landing_trajectory}}{\includegraphics[width=0.5\textwidth]{figures/traj_fig.pdf}}~
    \subcaptionbox{Position of spacecraft in the inertial frame\label{fig:pos_components}}{\includegraphics[width=0.5\textwidth]{figures/pos_fig.pdf}}
    \caption{Landing trajectory to asteroid Itokawa~\label{fig:position}}
\end{figure}

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one exampel view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~\cref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
From these tracked features it is possible to estimate the relative motion of the camera~\cite{szeliski2010}.
\Cref{fig:orbslam_localization} shows a visualization of the localization process from the imagery. 
Through monocular images it is not possible to compute the position of the camera relative to the inertial frame.
Rather, it is only possible to determine a camera pose accurate to an unknown scale factor. 
This limitation is intrinsic to the transformation of the three-dimensional scene onto the two-dimensional image plane~\cite{szeliski2010}.
However, it is possible to compute the relative motion between sequential images and we use this to estimate the motion of the camera.
\begin{figure}[htbp]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{Feature tracking visualization\label{fig:orbslam_mappoints}}{\includegraphics[width=0.5\textwidth]{figures/orbslam_mappoints.png}}~
    \subcaptionbox{Localization from monocular images\label{fig:orbslam_localization}}{\includegraphics[width=0.5\textwidth]{figures/orbslam_localization.png}}
    \caption{ORB-SLAM2 feature detection and localization from imagery~\label{fig:orbslam}}
\end{figure}
